\subsection{Ego}
%\begin{frame}
%	\frametitle{Who Am I ?}
%	\begin{itemize}
%		\item Louis Ledoux
%		\item research interests:
%			Computer Architecture: Floating-Point Units, Systolic Arrays, Matrix-Matrix Multiply (MMM) Units, GPUs, FPGAs
%Computer Arithmetic: Number Representations, Application-Specific Circuits, FloPoCo, Posit & IEEE754 Standards,
%Kulisch Accumulator, Accuracy and Energy Budgeting
%High Performance Computing: BLAS, GEMMs, Heterogeneous Workloads, Numerical Analysis, Supercomputing
%		\item education:
%			classe prepa integree
%			ESIR
%			UPC
%			soon post doc lyon insa with florent de dinechin
%
%		\item
%	\end{itemize}
%\end{frame}

\begin{frame}
	\frametitle{Who Am I? — Basic Info}
	\begin{itemize}
		\item \textbf{Name:} Louis Ledoux
		\item \textbf{Role:} PhD Candidate in Computer Architecture
		\item \textbf{Current Affiliation:} [Your University or Research Institute]
		\item \textbf{Contact and More:}
		\begin{itemize}
			\item [\href{https://example.com}{Website}] — Detailed CV, papers, projects, and more.
			\item Publications on \href{https://arxiv.org/}{arXiv} and other journals.
		\end{itemize}
		\item \textbf{Fun Fact:} Also an electronic music producer—attempting to optimize beats while optimizing circuits.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Who Am I? — Research Interests}
	\begin{itemize}
		\item \textbf{Computer Architecture:}
		\begin{itemize}
			\item Floating-Point Units, Systolic Arrays, Matrix-Matrix Multiply (MMM) Units
			\item GPUs, FPGAs, workload-specific accelerators
		\end{itemize}
		\item \textbf{Computer Arithmetic:}
		\begin{itemize}
			\item Number Representations, Application-Specific Circuits
			\item FloPoCo, Posit & IEEE 754 Standards
			\item Kulisch Accumulator, Accuracy and Energy Optimization
		\end{itemize}
		\item \textbf{High Performance Computing:}
		\begin{itemize}
			\item BLAS, GEMMs, Heterogeneous Workloads
			\item Numerical Analysis, Supercomputing
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Who Am I? — Education}
	\begin{itemize}
		\item \textbf{Integrated Preparatory Class:}
		\begin{itemize}
			\item Gained a strong foundation in mathematics and sciences.
		\end{itemize}
		\item \textbf{ESIR:}
		\begin{itemize}
			\item Engineer + Master's Degree, specializing in Computer Architecture.
		\end{itemize}
		\item \textbf{UPC Barcelona:}
		\begin{itemize}
			\item International experience enriching my knowledge in HPC and computer arithmetic.
		\end{itemize}
		\item \textbf{Coming Soon: Postdoc at INSA Lyon:}
		\begin{itemize}
			\item Collaborating with Florent de Dinechin on advanced floating-point arithmetic research.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Who Am I? — Hobbies}
	\begin{itemize}
		\item \textbf{Music Production:}
		\begin{itemize}
			\item I create electronic music, focusing on Intelligent Drum and Bass.
			\item Available under "et-al-records" on SoundCloud.
		\end{itemize}
		\item \textbf{Fusion of Work and Play:}
		\begin{itemize}
			\item Whether it's optimizing circuits or crafting soundscapes, precision is key.
		\end{itemize}
		\item \textbf{Outdoors:}
		\begin{itemize}
			\item Cycling and hiking — it’s good to step away from transistors and get some fresh air.
		\end{itemize}
	\end{itemize}
\end{frame}
